\phantomsection
\addcontentsline{toc}{chapter}{Acknowledgements}

\noindent \textbf{Acknowledgements}

This work is based on observations made with the Spitzer Space Telescope, which is operated by the Jet Propulsion Laboratory (JPL), California Institute of Technology (Caltech) under a contract with the National Aeronautics and Space Administration (NASA). This research made use of; the SIMBAD database and VizieR catalog access tools, operated at Centre de Donn\'ees astronomiques de Strasbourg, France \citep{VIZIER}; data products from the Two Micron All Sky Survey, which is a joint project of the University of Massachusetts and the Infrared Processing and Analysis Center (IPAC)/Caltech, funded by NASA and the National Science Foundation \citep{2MASS}; data products from the Wide-field Infrared Survey Explorer, which is a joint project of the University of California, Los Angeles, and JPL/Caltech, funded by NASA \citep{WISE}; the NASA/IPAC Infrared Science Archive, which is operated by the JPL, Caltech, under contract with NASA; and data from the European Space Agency (ESA) mission {\it Gaia}\footnote{\url{https://www.cosmos.esa.int/gaia}}, processed by the {\it Gaia} Data Processing and Analysis Consortium (DPAC)\footnote{ \url{https://www.cosmos.esa.int/web/gaia/dpac/consortium}}. Funding for the DPAC has been provided by national institutions, in particular the institutions participating in the {\it Gaia} Multilateral Agreement.

I want to acknowledge the community at the Vanderbilt-Fisk Bridge-to-the-Ph.D. and the Department of Physics \& Astronomy at Vanderbilt University for their consistent and ardent support in guiding young scientists like myself to achieve their dreams, especially Dr. Dina Stroud and Dr. Kelly Holley-Bockelmann.  I also want to thank my advisors, namely Dr. Keivan Stassun for nuturing with his mentorship since 2015, on both personal and professional levels. I give thanks to Dr. Peter Plavchan for helping me build my confidence as a scientist, and for being an integral part of helping me produce this thesis.

I want to thank my father, Gerald (Jerry) Galgano for inspiring in me at a very young age my love for astronomy, and my mother Gloria (Nancy) Galgano for never giving up on me through difficult times. I want to thank my sister Ashley Galgano for having a fervent drive in always aiding to reach my goals.